On centrality of orthogonal $\Kt$

### 2016-05-11 paper.tex
More fixes

Centrality of $\Kt$ is a corollary of the following variant of Quillen's local-global principle,
very much in the same fashion as the normality theorem for the elementary subgroup is a corollary of Quillen's local-global principle for $\Ko$.
\begin{tm}[``Quillen's LG-principle for $\Kt$''] \label{tm:lg-principle} 
Let $\Phi$ be an irreducible simply-laced root system of rank $\geq 3$ and $R$ be arbitrary commutative ring.
Then an element $g\in\St(\Phi,\,R[X])$ satisfying $g(0)=1\in\St(\Phi,\,R)$ is trivial in $\St(\Phi,\,R[X])$
if and only if the images $\lambda_M^*(g)\in\St(\Phi,\,R_M[X])$ of $g$ under localisation maps $\lambda_M\colonR\to R_M$ are trivial for all maximal ideals $M\trianglelefteq R$. \end{tm}
For the proof of the claim that \cref{tm:lg-principle} follows from \cref{tm:centrality} we refer the reader to the proof of Theorem~1 in \cite{SCh} which works verbatim in our case.

The assertion of \cref{tm:lg-principle} was known previously in the following two situations:
\begin{itemize}
 \item in the case $\Phi=\rA_\ell$, $\ell\geq 4$ it was proved by Tulenbaev, the proof see~\cite[Theorem~2.1]{Tul}
 \item $\Phi=\rE_\ell$, $\ell=6,7,8$ and the second-named author
\end{itemize}
Thus, the special cases $\Phi=\rA_3$ and $\Phi=\rD_\ell$, $\ell\geq 4$ of \cref{tm:lg-principle} are new and have not been known before.
We also notice that a symplectic counterpart of~\cref{lg-principle} was demonstrated recently by the first-named author.

On the other hand, the special case 
includes as a special case both and~\cite[Theorem~2]{SCh} in which
the cases were studied, respectively.

As a yet another motivation for ??? we mention that

There are known counterexamples to centrality of $\Kt$ in rank $2$ (see~\cite{W}).
This shows that our assumption on the rank of $\Phi$ in \cref{tm:lg-principle} is strict.

>>>>

Centrality of $\Kt$ follows the following the following analogue of Quillen's local-global principle,
very much in the same fashion as the normality theorem for the elementary subgroup follows from Quillen's local-global principle for $\Ko$, cf.~\cite[Theorem~3.1]{Basu05}.
\begin{tm}[``Quillen's LG-principle for $\Kt$''] \label{tm:lg-principle} 
Let $\Phi$ be an irreducible simply-laced root system of rank $\geq 3$ and $R$ be arbitrary commutative ring.
Then an element $g\in\St(\Phi,\,R[X])$ satisfying $g(0)=1\in\St(\Phi,\,R)$ is trivial in $\St(\Phi,\,R[X])$
if and only if the images $\lambda_M^*(g)\in\St(\Phi,\,R_M[X])$ of $g$ under localisation maps $\lambda_M\colon R\to R_M$ are trivial for all maximal ideals $M\trianglelefteq R$. \end{tm}
For the proof of the claim that \cref{tm:lg-principle} follows from \cref{tm:centrality} we refer the reader to the proof of Theorem~1 in \cite{SCh} (which works verbatim in our situation).

\cref{tm:lg-principle} was known previously in the following two special cases.
\begin{itemize}
 \item In the case $\Phi=\rA_\ell$, $\ell\geq 4$ it was proved by Tulenbaev, see~\cite[Theorem~2.1]{Tul}. 
 \item In the case $\Phi=\rE_\ell$, $\ell=6,7,8$ it was obtained in~\cite{SCh} by the second-named author.
\end{itemize}
Thus, the special cases $\Phi=\rA_3$ and $\Phi=\rD_\ell$, $\ell\geq 4$ of \cref{tm:lg-principle} are new and have not been known before.

Notice that the first-named author has recently established the local-global principle for $\Kt(\rC_\ell, R)$ under the assumption $\ell\geq 3$.
The main shortcoming of Tulenbaev's proof is that it left the case $\Phi=\rA_3$ unsettled.

Since there are known counterexamples to centrality of $\Kt$ in the rank $2$ case (see~\cite{W}), our assumption on the rank of $\Phi$ in \cref{tm:lg-principle} can not be weakened.
